BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-01-14 tex/1-intro.tex
Add plan of the future into

\section{Intro}

Web archiving is the process of harvesting and gathering web content in order to safely preserve it for posterity.
As the volume and importance of the information on the World Wide Web increases, web archiving becomes more and more relevant and its importance becomes clearer.
Web crawlers are an essential part of web archiving, allowing for automated capturing of web resources.
An efficient and accurate web crawler is the first crucial step to successful digital preservation.

@@

*** Do we need to present issues in current solutions here? Is it needed? Can we write it in "Related Work" instead? ***

Our solution aims to tackle the challenges and constraints described above by employing a series of techniques and algorithms to harvest modern weblogs in a high-quality, accurate and efficient manner.
We base our crawler on one of the most common and standard characteristics of blogs: web feeds.
Explain:
\begin{enumerate}
  \item what feeds are, and what we use them for (discovery, extraction)
  \item the use of HTML + XPATH
  \item the use of efficient string similarity
  \item the use of javascript rendering
\end{enumerate}

The rest of the paper is organized as follows: Related work is presented in Section 2; the algorithms we developed to extract blog post articles, authors, dates and comments are detailed in Section 3; in section 4 we give an overview of the different techniques used in our crawler; evaluation experiments are described and commented in Section 5. We finally conclude and present future work in Section 6.

% \comment{(from wikipedia) The largest web archiving organization based on a bulk crawling approach is the Internet Archive which strives to maintain an archive of the entire Web. National libraries, national archives and various consortia of organizations are also involved in archiving culturally important Web content. Commercial web archiving software and services are also available to organizations who need to archive their own web content for corporate heritage, regulatory, or legal purposes.}

% \comment{Aims and contributions of this work. Example from my last paper to see the format:\\
% http://purl.pt/24107/1/iPres2013\_PDF/\\
% CLEAR\%20a\%20credible\%20method\%20to\%20\\
% evaluate\%20website\%20archivability.pdf}

% \comment{Semi-structured nature of Web pages\\
% Labeled ordered rooted trees\\
% XML Path Language(XPath)}

% \TODO{should we explain here that article is the actual content (text) of a blog post? Or is it already clear enough? -> I don't know. I used "blog post content" as "article + title + author + date + comments" in other sentences but it might be good to say somewhere that "blog post article" refers to the "core textual content of a blog post".}

% \TODO{Is it ok to call this "the BlogForever cralwer", given that it will be the 3rd implementation?}

% Intro contents (more or less)
% \begin{enumerate}
%   \item Introduce the importance for blog preservation
%   \item Explain the difficulties in harvesting blogs
%   \item Explain why open source and Invenio
%   \item Introduce the blog crawler
% \end{enumerate}

% Challenges and constraints:
% \begin{enumerate}
%   \item size of blogosphere (Dealing with large volumes of data)
%   \item heterogeneous nature of different publishing platforms
%   \item ever-changing structure
%   \item dynamically created content using modern web technologies.
%   \item complexity in parsing blogs from unstructured data to structured information.
%   \item programmatic access to blog content unavailable
%   \item unpredictable publishing rate --> scalability
%   \item Providing a high degree of automation
% \end{enumerate}

>>>>

\section{Introduction}

This will be reorganized like this:\\
paragraph 1:\\
- Blog disappear every day, Some of them are important\\
- In contrast to newspaper and centralized services like FaceBook and Twitter there are no standards and no authorities to backup blogs\\
- Yet, blogs are an important part of today's web (number, adoption by academics and organizations)\\
\\
paragraph 2:\\
- Challenges (Now starts with "The blogosphere is a massive...")\\
\\
paragraph 3:\\
- Web feed, why they are so handy (merged with "Blogs are strongly associated with web feeds...")

Web archiving is the process of harvesting and gathering web content in order to safely preserve it for posterity. As the volume and importance of the information on the World Wide Web increases, web archiving becomes more and more relevant and its importance becomes clearer. \comment{too early imo- Web crawlers are an essential part of web archiving, allowing for automated capturing of web resources. An efficient and accurate web crawler is the first crucial step to successful digital preservation.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contributions and Overview}
We present the BlogForever Crawler, a key component of the BlogForever platform responsible for traversing, extracting content and monitoring updates of blogs.
Our contributions are in particular:

\begin{itemize}
  \item We present a new generic algorithm to build extraction from a set of pages and target content. We then derive an optimized reformulation tied to a particular string similarity and show that this reformulated algorithm has a linear time complexity.
  \item We show how to use this algorithm to extract blog articles, and how it can be adapted to extract authors, publication dates and comments.
  \item We present the overall crawler architecture and the specific components we implemented to efficiently traverse blogs. We explain how our design allows for both modularity and scalability.
  \item We show who use make use of a complete web browser to render JavaScript powered web pages before processing them. This step allows our crawler to effectively harvest blogs build with modern technology, such at the increasingly popular third-party commenting systems.
  \item We present and analyze performance results of our algorithm in terms of extraction success rates and execution time. A comparison is made with three state-of-the-art article extraction algorithms.
\end{itemize}

Although our crawler implementation is integrated with the BlogForever platform, the presented techniques and algorithms can be used in other applications related to Wrapper Generation and Web Data Extraction.

### 2014-01-14 tex/3-algorithms.tex
Improvements to the Introduction section
Add plan of the future into

This section explains in detail the algorithm we developed to extract blog posts articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of a blog \comment{Does "all posts of a blog" need a better formulation? Maybe "across/throughout a blog"?}.Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.

>>>>

This section explains in detail the algorithm we developed to extract blog post articles as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules which are applicable to all posts of throughout a blog. Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.

### 2014-01-14 tex/main.tex
Add algo1.
Pull out algos and tables, 3-algorithms close to done.
up
Time complexity.
Linear algo started.
Algorithm 2 done.
Reread it all.
Minor fixes in captions + some of variations subsection.
Variations done.
Add first gnuplot figure.
Fix compilation errors with gnuplot and commath.
Re-read all the paper, lots of rephrasing.
Remove left char that breaks the compilation.
Eval++
Minor fixes, add main.pdf under version control.
Solve some \cite TODOs.
Un-draft build.
Up
Add plan of the future into

\documentclass{acm_proc_article-sp}

\usepackage[autostyle=false, style=english]{csquotes}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{quoting}
\usepackage{url}
\usepackage{sepfootnotes}

\newfootnotes{A}
\MakeOuterQuote{"}
\quotingsetup{vskip=0pt,font={itshape}}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}

\newcommand{\TODO}[1]{\emph{\color{red} TODO: #1}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\surl}[1]{\urlstyle{ff}\url{#1}}

@@

  \title{BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs}

@@

  \author{
  % 1st. author
  \alignauthor
  Olivier Blanvillain\\
         \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
         \affaddr{1014 Lausanne, Switzerland}\\
         \email{\surl{olivier.blanvillain@epfl.ch}}
  % 2nd. author
  \alignauthor
  Nikos Kasioumis\\
         \affaddr{European Organization for Nuclear Research (CERN)}\\
         \affaddr{1211 Geneva 23, Switzerland}\\
         \email{\surl{nikos.kasioumis@cern.ch}}
  % 3rd. author
  \alignauthor
  Vangelis Banos\\
         \affaddr{Department of Informatics}\\
         \affaddr{Aristotle University of Thessaloniki, Greece}\\
         \email{\surl{vbanos@gmail.com}}
  }

  \maketitle

@@

  \keywords{Web archiving, Web crawling, ...}

  \input{1-intro.tex}
  \input{2-related-work.tex}
  \clearpage
  \input{3-algorithms.tex}
  \clearpage
  \input{4-techniques.tex}
  \clearpage
  \input{5-evaluation.tex}
  \clearpage
  \input{6-conclusion-and-future-work.tex}

  \bibliographystyle{abbrv}
  \bibliography{main}

>>>>

% \documentclass[draft]{acm_proc_article-sp}
\documentclass{acm_proc_article-sp}

\usepackage[ruled, vlined]{algorithm2e}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[autostyle=false, style=english]{csquotes}
\usepackage[usenames,dvipsnames]{color}
\usepackage[justification=centering]{caption}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{gnuplottex}
\usepackage{pifont}
\usepackage{quoting}
\usepackage{url}
\usepackage{sepfootnotes}
\usepackage{setspace}
\usepackage[pdfpagelabels=false]{hyperref}
\usepackage{hypcap}

\MakeOuterQuote{"}
\newfootnotes{A}
\quotingsetup{vskip=0pt,font={itshape}}
\setenumerate{noitemsep,topsep=0pt,parsep=2pt,partopsep=0pt}
\setitemize{noitemsep,topsep=0pt,parsep=4pt,partopsep=0pt}
\setlength\floatsep{1.25\baselineskip plus 3pt minus 2pt}
\setlength\textfloatsep{1.25\baselineskip plus 3pt minus 2pt}
\setlength\intextsep{1.25\baselineskip plus 3pt minus 2 pt}
\def\algorithmautorefname{Algorithm}
\graphicspath{{img/}}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\newcommand\TODO[1]{\emph{\color{Red} TODO: #1}}
\renewcommand\comment[1]{\emph{\color{Gray}<#1>}}
\newcommand\edit[1]{\emph{\color{Green}<#1>}}
\newcommand\code[1]{\texttt{#1}}
\newcommand\coderef[1]{\texttt{\ref{#1}}}
\newcommand\stringliteral[1]{\texttt{\char`\"#1\char`\"}}
\newcommand\len[1]{|#1|}
\newcommand\set[1]{\{#1\}}
\newcommand\surl[1]{\urlstyle{ff}\url{#1}}
\newcommand\Oof[1]{$\mathcal{O}(#1)$}

@@

  \title{BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs}

@@

  \author{
  % 1st. author
  \alignauthor
  Olivier Blanvillain\\
         \affaddr{École polytechnique fédérale de Lausanne (EPFL)}\\
         \affaddr{1015 Lausanne, Switzerland}\\
         \email{\surl{olivier.blanvillain@epfl.ch}}
  % 2nd. author
  \alignauthor
  Nikos Kasioumis\\
         \affaddr{European Organization for Nuclear Research (CERN)}\\
         \affaddr{1211 Geneva 23, Switzerland}\\
         \email{\surl{nikos.kasioumis@cern.ch}}
  % 3rd. author
  \alignauthor
  Vangelis Banos\\
         \affaddr{Department of Informatics}\\
         \affaddr{Aristotle University of Thessaloniki, Greece}\\
         \email{\surl{vbanos@gmail.com}}
  }

  \hypersetup{pageanchor=false}
  \maketitle

@@

  \keywords{Web crawling, Web Data Extraction, Wrapper Generation, Web archiving, ...}

  \input{algos.tex}
  \input{tables.tex}
  \input{1-intro.tex}
  \input{2-related-work.tex}
  \clearpage
  \input{3-algorithms.tex}
  \clearpage
  \input{4-techniques.tex}
  \clearpage
  \input{5-evaluation.tex}
  \clearpage
  \input{6-conclusion-and-future-work.tex}

  \bibliographystyle{abbrv}
  \bibliography{main,manual}
